---
title: "The **viabilitymetrics** package: A brief introduction"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[LE,RO]{\slshape \rightmark}
- \fancyfoot[C]{\thepage}
- \usepackage{hyperref}
- \hypersetup{colorlinks=true}
- \hypersetup{linktoc=all}
- \hypersetup{linkcolor=blue}
- \usepackage{pdflscape}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \fancyhead[LO,RE]{The viabilitymetrics package{:} A brief introduction}
output:
  pdf_document:
    dev: cairo_pdf
    fig_caption: no
  html_document:
    df_print: paged
csl: frontiers.csl
bibliography: REFERENCES.bib
toc: no
vignette: |
  %\VignetteIndexEntry{Introduction}
  %\usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown_notangle}
---
\begin{center}
 {\it J. Aravind, S. Vimala Devi, J. Radhamani and Kalyani Srinivasan}
\end{center}

\begin{center}
 ICAR-National Bureau of Plant Genetic Resources, New Delhi
\end{center}

\begin{center}
`r Sys.Date()`
\end{center}

\begin{center}
\vspace{6pt}
\hrule
\end{center}

```{r, echo = FALSE}
knitr::opts_chunk$set(
  comment = "",
  fig.cap = ""
)
```


\tableofcontents

## Overview

## Installation
The package can be installed using the following functions:

```{r, eval=FALSE}
# Install from CRAN
install.packages('viabilitymetrics', dependencies=TRUE)

# Install development version from Github
devtools::install_github("aravind-j/viabilitymetrics")
```

Then the package can be loaded using the function
```{r}
library(viabilitymetrics)
```


## Viability constants

\rowcolors{2}{gray!25}{white}
\renewcommand{\arraystretch}{1.3}

```{r, echo = FALSE}
library(viabilitymetrics)
load("vc.rda")

vc$Species <- gsub("\\*", "&#42;", vc$Species)
vc$Species <- paste("*", vc$Species, "*", sep = "")
vc$Species <- gsub("×", "$\\\\times$", vc$Species)
vc$Species <- gsub("(\\*)(.+)(cvs.|spp.)(\\*)", "\\1\\2\\4\\3", vc$Species)
vc$Species <- gsub("(\\*)(.+)(cv.)(\\s.+)(\\*)", "\\1\\2\\5\\3\\4", vc$Species)
vc$Species <- gsub("(\\*)(.+)(\\s)(ssp.)(\\s)(.+)(\\*)",
                   "\\1\\2\\*\\3\\4\\5\\*\\6\\7", vc$Species)
vc$Species <- gsub("(&#42;)(\\*)", "\\2\\1", vc$Species)
vc$Species <- gsub("(\\()(.+)(\\))(\\*)", "\\4\\1\\2\\3", vc$Species)

# vc$Species <- gsub("(\\s)(subsp.)(\\s)", "\\1\\*\\2\\*\\3", vc$Species)
# vc$Species <- gsub("(\\s)(convar.)(\\s)", "\\1\\*\\2\\*\\3", vc$Species)
# vc$Species <- gsub("(\\s)(var.)(\\s)", "\\1\\*\\2\\*\\3", vc$Species)

ind <- grepl("*Cucurbita pepo subsp. pepo convar. pepo var. styriaca*",
             vc$Species)
vc[ind,]$Species <- "*Cucurbita pepo* subsp. *pepo* convar. *pepo* var. *styriaca*"



vc$Reference <- gsub("\\[|\\]", "", vc$Reference)

colnames(vc) <- c("Index", "Species", "K~E~", "C~W~", "C~H~", "C~Q~", "Reference")
pander::pander(vc, style = 'multiline', justify = c('left'),
               split.table = Inf, keep.line.breaks = TRUE,
               use.hyphening = FALSE, missing = "")
```
&#42; Viability constants are derived from storage experiment at a single temperature. C~H~ and C~Q~ here are the universal temperature coefficients (0.0329 and 0.000478 respectively).

## Citing `viabilitymetrics`

```{r, echo = FALSE, collapse = TRUE}
suppressMessages(cit <- citation("viabilitymetrics"))
yr <- format(Sys.Date(), "%Y")
cit[1]$year <- yr
oc <- class(cit)

cit <- unclass(cit)
attr(cit[[1]],"textVersion") <- gsub("\\(\\)",
                                     paste("\\(", yr, "\\)", sep = ""),
                                     attr(cit[[1]],"textVersion"))
class(cit) <- oc
cit
```


## Session Info

```{r}
sessionInfo()
```

## References
